---
title: "Homework 2"
author: "Mari Sanders"
output: github_document
---
# Problem 1 

## a) 

This can be solved using a binomial distribution because there is a fixed number of trials and there are only two possible outcomes, either the individual had at least 1 dental checkup or not. 

To solve this problem, we then know that X ~ Binomial(56,0.73). 
The formula of a binomial distribution is \(P(X= x) = {n \choose x}p^x(1-p)^{n-x} = \frac{n!}{x!(n-x)!}p^x(1-p)^{n-x}\)

In this case, we have to do 
\(P(X = 40)= {56 \choose 40}0.73^{40}(1-(0.73))^{56-40} = \frac{56!}{40!(56-40)!}(0.73)^{40}(1-0.73)^{56-40} = 0.1133\)

```{r}
exactly_40 <- dbinom(40,size = 56, prob = 0.73)
```


## b) 


```{r}
at_least_40 <- pbinom(q = 39, size = 56, prob = 0.73, lower.tail = FALSE)
```

\(P(X \geq 40) = `r at_least_40`\)

## c)

It would not be good to approximate this with a Poisson distribution because n = 56, which is not greater than 100. Also the probability of success is 0.73, and it should be less than 0.01 for Poisson to be a good approximation. 

However, a normal approximation would be valid for this situation because \(np = (0.73)(56)=40.88\geq 10\) and \(n(1-p) = 56(1-0.73) = 15.12 \geq 10\). Therefore, we can approximate this as a normal distribution. 

We need to find the expected value and standard deviation of the normal distribution 

\(E(X) = \mu = np = (0.73)(56) = `r 0.73 * 56`\)

\(Var(x) = \sigma = \sqrt{np(1-p)} = \sqrt{(0.73)(56)(1-0.73)} = `r sqrt(0.73)*(56)*(1-0.73)`\) 

```{r}
mu <- 0.73 * 56 
sd <- sqrt(.73 * 56 * .27)

exactly_40_normal <- dnorm(40, mean = mu, sd =  sd)
```


```{r}
at_least_40_normal <- pnorm(40, mean = mu, sd = sd, lower.tail = FALSE)

```

The difference between the normal distribution and the binomial distribution probability for $P(X = 40)$ = 
`r abs(exactly_40_normal - exactly_40)`. The difference between the normal distribution and the binomial distribution for $P(X \geq 40)$ = `r abs(at_least_40_normal - at_least_40)`.
. 

The normal approximation for exact probabilities are closer than those for \(P(X \geq x)\) but still is a good approximation. 

## d)

\(E(X) = \mu = np = (0.73)(56) = `r 0.73 * 56`\)

I expect about 41 individuals to have at least one dental checkup. 

## e)

\(Var(x) = \sigma = \sqrt{np(1-p)} = \sqrt{(0.73)(56)(1-0.73)} = `r sqrt(0.73)*(56)*(1-0.73)`\) 

The standard deviation of the number of individuals who will have at least one dental checkup is about 14. 

# Problem 2 

## a) 

Poisson Distribution: $P(X = x) = \frac{\lambda^xe^{-\lambda}}{x!}$

Then $P(X < 3) = P(X = 0) + P(X = 1) + P(X = 2)$

$P(X = 0) = \frac{6^0e^{-6}}{0!} = .0025$

$P(X = 1) = \frac{6^1e^{-6}}{1!} = 0.0145$

$P(X = 2) = \frac{6^2e^{-6}}{2!} = 0.045$

$P(X < 3) = 0.0025 + 0.0145 + 0.045 = 0.062$

Want to find $P(X < 3)$
```{r}
fewer_than_3_tornadoes <- ppois(2, lambda = 6)
```

The probability of seeing less than 3 tornadoes is `r fewer_than_3_tornadoes`

## b) 
Want to find $P(X = 3)$
```{r}
exactly_3_tornadoes <- dpois(3, lambda = 6)
```

The probability of having exactly 3 tornadoes is `r exactly_3_tornadoes`

## c) 
Want to find $P(X \geq 3)$
```{r}
more_than_3_tornadoes <- ppois(3, lambda = 6, lower.tail = FALSE)
```

The probability of having more than three tornadoes is `r more_than_3_tornadoes`

# Problem 3 

## a) 

$H_0: \mu = 137$

$H_A: \mu > 137$

```{r}
pop_mean <- 128
pop_sd <- 10.2
probability_greater_137 <-  1 - pnorm(137, mean = pop_mean, sd = pop_sd)
```

The probability that a randomly selected American male between 20 and 29 has a systolic blood pressure above 137.0 is `r probability_greater_137`

## b) 

```{r}
n <- 50
sample_se <- (10.2/sqrt(50))
prob_less_125 <- pnorm(125, mean = pop_mean, sd = sample_se)

```

The probability that the sample mean for blood pressure of 50 males between 20 and 29 years old will be less than 125 is `r prob_less_125`. 

## c) 

```{r}
z_90 <- qnorm(0.90)

n <- 40

se <- pop_sd/sqrt(40)

percentile_90 <- 
  pop_mean + z_90 * se
```

The 90th percentile of the sampling distribution of the sample mean X for a sample size of 40 is `r percentile_90`

# Problem 4

## a) 

```{r}
sample_mean <- 80 
sample_sd <- 10
n <- 40 

SE <- sample_sd / sqrt(n)

critical_val <- qt(1 - (0.05/2),df = 39)

margin_of_error <- critical_val*SE

lower_bound <- sample_mean - margin_of_error
lower_bound
upper_bound <- sample_mean + margin_of_error
upper_bound

```



## b) 

We are 95% confident that the mean pulse of young women suffering from Fibromyalgia falls between (`r lower_bound`, `r upper_bound`)

## c) 

$H_0: \mu = 70$
$H_A: \mu \neq 70$

```{r}
mu <- 80
standard_error <- 10
se <- (standard_error/sqrt(40))
critical_val_2 <- qt(1 - (0.01/2), df = 39)

t_value <- (80 - 70) / se

p_value <- 2 * pt(t_value, 39, lower.tail = FALSE)
```

Reject the null hypothesis that $\mu=70$ because the p-value is small. This means that the mean pulse of young women suffering from Fibromyalgia is not equal to 70.  

