---
title: "Homework 2"
author: "Mari Sanders"
output: html_document
---
# Problem 1 

## a) 

This can be solved using a binomial distribution because there is a fixed number of trials and there are only two possible outcomes, either the individual had at least 1 dental checkup or not. 

To solve this problem, we then know that X ~Binomial(56,0.73). 
The formula of a binomial distribution is \(P(X= x) = {n \choose x}p^x(1-p)^{n-x} = \frac{n!}{x!(n-x)!}p^x(1-p)^{n-x}\)

In this case, we have to do 
\(P(X = 40)= {56 \choose 40}0.73^{40}(1-(0.73))^{56-40} = \frac{56!}{40!(56-40)!}(0.73)^{40}(1-0.73)^{56-40} = 0.1133\)

```{r}

```


## b) 

\(P(X \geq 40) = 1-P(X \leq 39)\)

```{r}
at_most_39 <- pbinom(q = 39, size = 56, prob = 0.73)

at_least_40 <- 1 - at_most_39
```

\(P(X \geq 40) = `r 1 - at_most_39`\)

## c)

It would not be good to approximate this with a Poisson distribution because n = 56, which is not greater than 100. Also the probability of success is 0.73, and it should be less than 0.01 for Poisson to be a good approximation. 

However, a normal approximation would be valid for this situation because \(np = (0.73)(56)=40.88\geq 10\) and \(n(1-p) = 56(1-0.73) = 15.12 \geq 10\). Therefore, we can approximate this as a normal distribution. 

We need to find the expected value and standard deviation of the normal distribution 

\(E(X) = \mu = np = (0.73)(56) = `r 0.73 * 56`\)

\(Var(x) = \sigma = \sqrt{np(1-p)} = \sqrt{(0.73)(56)(1-0.73)} = `r sqrt(0.73)*(56)*(1-0.73)`\) 

```{r}
mu <- (0.73)*(56) 
sd <- sqrt(0.73)*(56)*(1-0.73)
pnorm(40, mean = mu, sd = sd)
```

```{r}
1 - pnorm(40, mean = mu, sd = sd)

```

## d)

\(E(X) = \mu = np = (0.73)(56) = `r 0.73 * 56`\)

I expect about 41 individuals to have at least one dental checkup. 

## e)

\(Var(x) = \sigma = \sqrt{np(1-p)} = \sqrt{(0.73)(56)(1-0.73)} = `r sqrt(0.73)*(56)*(1-0.73)`\) 

The standard deviation of the number of individuals who will have at least one dental checkup is about 14. 

# Problem 2 

## a) 

```{r}

```

# Problem 3 

## a) 

## b) 

## c) 

# Problem 4

## a) 



